Analyzing Coopetition Strategies of Services within Communities

### 2012-11-26 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changed 3 in a row graph sizes from 550 to 500
Updated Text

\begin{figure}%[h]
\centering
\includegraphics[scale=0.275]{graphbgtmed3set.eps}
\includegraphics[scale=0.275]{graphbgthigh.eps}
\includegraphics[scale=0.275]{graphbgtveryhigh.eps}
\caption{High membership fees or less task income impacts on different selection strategies, (a) medium membership fee, (b) high membership fee, (c) very high membership fee} \label{membership_fee_graph}
\end{figure}

In figure \ref{membership_fee_graph} we analyse the scenario where membership fee is high which is analogous to sitations where task income is low. For any reason our web services may need to stay in a particular comuunity with economic downtimes. We need verify how well the web services can perform in these situations. \ref{membership_fee_graph} part (a) depicts the results in normal scenario. In part (b) we have inceased the membership fee to the high ammount of 5 per run. Web services will need to pay 5 bucks on each iteration of tasks being offered. As results the strategic coopetetive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace. In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer. It might not berational for selfish self-interet web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these comuunities. As reseults show the random and all compete strategies make webservices bank deplete in no time. However our strategic coopetetive decision making process loses budget in a slower pace.

@@

\begin{figure}%[h]
\centering
\includegraphics[scale=0.275]{graphtaskdone.eps}
\includegraphics[scale=0.275]{graphtasksatisfaction.eps}
\includegraphics[scale=0.275]{graphavgqostask.eps}
\caption{Overall performance from comunity point of view, (a) Total Number of tasks succesfuly done, (b) Ratio of tasks satisfied with required QoS, (c) Average QoS of performed tasks} \label{graph_task}
\end{figure}

The web services are selfish, self interested agents. They try to maximise their own utiliy. Now we analyse how their strategy effects the social welfare or from user and community point of view how good the tasks are being performed. This directly affects user satisfation and community reputation in general. The Higher  quality and quantity of tasks perfromed leads to higher user satisfaction for the community which results in better reputaiton for the community. The results in figure \ref{graph_task} shows the quality of quantity of tasks being done successfuly in three communities adopting the three different mentioned strategy decision algorithms. Part(a)and(b) depicts the number tasks succesfuly done. When web services are not capable of performing tasks alone and decide to compete for tasks with high QoS requirements they usually fail to perform the task how ever if they opt for cooperating although they have less income, they have higher chance of performing tasks collabratively with other web serives. Figure \ref{graph_task}Part (b) shows the probablilty of successfully performin tasks. As results suggest web services using our coopetetive strategy when deciding whether to compete or cooperate have higher chance of tasks to be done than random or all compete strategies. The quality of tasks performed are depicted in Figure \ref{graph_task} Part (c). It shows the average QoS of tasks perfromed which are finished and done sucessfuly. Colabrating increases the performed QoS of tasks, therefore forming collabrative groups improves user satisfaction. As results suggest, the coopetetive community outperforms the random and all compete communities in quality of tasks performed.

We conclude out analysis by discussing how effective our cooperative decision making process is by comparing the final utility of our agents here the end budget our webservices have while deviating from our strategy adopted by an agent which can be either compete or cooperate to the other one. In \ref{graph_dev} part (a) we randomly made the web services deviate from the calculated strategy. As the results depict, the more web services deviate from cooperative strategy the more they less budget they gain. Figure \ref{graph_dev} part (b) we pick one random webservice and once simulate the scenario with its default cooperative strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our cooperative strategy suggested to cooperate or vise versa. We run this 50 times and at the end we check their budget and see if they gain more by deviating or not. We did this for one single deviation to ten different deviations in lifetime of a web service in community. As results indicate with high probability our cooperative strategy yields higher budgets at the end for web services.

>>>>

\begin{figure}%[h]
\centering
\includegraphics[scale=0.302]{graphbgtmed3set.eps}
\includegraphics[scale=0.302]{graphbgthigh.eps}
\includegraphics[scale=0.302]{graphbgtveryhigh.eps}
\caption{High membership fees or less task income impacts on different selection strategies, (a) medium membership fee, (b) high membership fee, (c) very high membership fee} \label{membership_fee_graph}
\end{figure}

In figure \ref{membership_fee_graph} we analyze the scenario where membership fee is high which is analogous to situations where task income is low. For any reason our web services may need to stay in a particular community with economic downtimes. We need verify how well the web services can perform in these situations. \ref{membership_fee_graph} part (a) depicts the results in normal scenario. In part (b) we have increased the membership fee to the high amount of 5 units per run. Web services will need to pay 5 units on each iteration of tasks being offered. As results the strategic coopetitive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace. In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer. It might not be rational for selfish self-interest web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these communities. As reseults show the random and all compete strategies make web services bank deplete in no time. However our strategic coopetetive decision making process loses budget in a slower pace.

@@

\begin{figure}%[h]
\centering
\includegraphics[scale=0.302]{graphtaskdone.eps}
\includegraphics[scale=0.302]{graphtasksatisfaction.eps}
\includegraphics[scale=0.302]{graphavgqostask.eps}
\caption{Overall performance from comunity point of view, (a) Total Number of tasks succesfuly done, (b) Ratio of tasks satisfied with required QoS, (c) Average QoS of performed tasks} \label{graph_task}
\end{figure}

The web services are selfish, self interested agents. They try to maximise their own utiliy. Now we analyse how their strategy effects the social welfare or from user and community point of view how good the tasks are being performed. This directly affects user satisfation and community reputation in general. The Higher  quality and quantity of tasks perfromed leads to higher user satisfaction for the community which results in better reputaiton for the community. The results in figure \ref{graph_task} shows the quality of quantity of tasks being done successfuly in three communities adopting the three different mentioned strategy decision algorithms. Figure \ref{graph_task} Part (a) and (b) depicts the number tasks succesfuly done. When web services are not capable of performing tasks alone and decide to compete for tasks with high QoS requirements they usually fail to perform the task how ever if they opt for cooperating although they have less income, they have higher chance of performing tasks collabratively with other web serives. Figure \ref{graph_task}Part (b) shows the probablilty of successfully performin tasks. As results suggest web services using our coopetitive strategy when deciding whether to compete or cooperate have higher chance of tasks to be done than random or all compete strategies. The quality of tasks performed are depicted in Figure \ref{graph_task} Part (c). It shows the average QoS of tasks perfromed which are finished and done sucessfuly. Colabrating increases the performed QoS of tasks, therefore forming collabrative groups improves user satisfaction. As results suggest, the coopetetive community outperforms the random and all compete communities in quality of tasks performed.

We conclude out analysis by discussing how effective our cooperative decision making process is by comparing the final utility of our agents here the end budget our web services have while deviating from our strategy adopted by an agent which can be either compete or cooperate to the other one. In \ref{graph_dev} part (a) we randomly made the web services deviate from the calculated strategy. As the results depict, the more web services deviate from cooperative strategy the more they less budget they gain. Figure \ref{graph_dev} part (b) we pick one random web service and once simulate the scenario with its default cooperative strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our cooperative strategy suggested to cooperate or vice versa. We run this scenario 50 times and at the end we check their budget and see if they gain more by deviating or not. We did this for one single deviation to ten different deviations in lifetime of a web service in community. As results indicate with high probability our cooperative strategy yields higher budgets at the end for web services.
